\documentclass{documentation}

\usepackage{minitoc}

\title{eMAGma Package}

\author{Joshua Maglione}
\address{Colorado State University}
\email{josh.maglione@gmail.com}

\author{James B. Wilson}
\address{Colorado State University}
\email{james.wilson@colostate.edu}

\version{1.1}
\date{\today}
\copyrightyear{2016}

%-----------------------------------------------------------------------------
\begin{document}

\frontmatter

\dominitoc
\maketitle
\tableofcontents

\mainmatter

\chapter{Introduction}

This chapter discusses Magma operations with multilinear algebra.
Wherever possible we follow the conventions in use in physics 
\cite{Weyl}*{Chapter V}, differential geometry 
\cite{Lee:geom}*{Chapter 10}, and algebra \cite{Landsberg:tensors}.
Necessary categorical formalism is drawn largely from
\cite{Wilson:division}.  The package covers:
\begin{enumerate}
\item Tensors and multilinear functions and their associated groups and algebras.
\item Spaces of tensors.
\item Categories of tensors and tensor spaces.
\item Exceptional tensors of octonions and Jordan algebras
\end{enumerate}

\section{Overview}
Throughout $\rightarrowtail$ denotes multilinear maps 
$[\cdot]:U_v\times \cdots \times U_1\rightarrowtail U_0$ of
$K$-modules $\{U_v,\dots,U_0\}$ known as the {\em frame} of a 
multilinear map or tensor.  
The module $U_0$ is reserved for the codomain which inturn makes
reverse indexing the simplest notation.
Every tensor in Magma is treated as an element of a tensor space.
By default a universal tensor space:
\begin{align*}
	\hom_K(U_v,\dots,\hom_K(U_1,U_0)\cdots).
\end{align*} 
In Magma, the tensor space is what determines the associated
multilinear function of a given tensor $T$.  
Evaluation of $T$ mimics a map
$U_v\times \cdots \times U_1\to U_0$, for instance, ${\tt	< u_v,\dots,u_1> @ T;}$.
Special attention is given to bilinear maps 
$*:U_2\times U_1\rightarrowtail U_0$
including the ability to use infix notation ${\tt u_2*u_1}$.
Tensor spaces have type {\tt TenSpc} and behave like modules 
in that they have subspaces and quotient spaces.  Tensors have type 
{\tt TenSpcElt} and behave similar to Magma matrices.


A library of commonly used exceptional tensors is provided.
These include octonion algebras and exceptional Jordan algebras.
 
Tensor categories, type {\tt TenCat}, tell Magma how to interpret the
contents of a tensor space.  For example, one tensor category treats a 
$(d\times d)$-matrix $F$ over a field $K$ as a linear map $K^d\to K^d$,
another assigns the same matrix to a bilinear form 
$K^d\times K^d\rightarrowtail K$.  Functors are provided to change
tensor categories and to define standard categories.  

\section{Verbose Printing and Version}

We have included intrinsics to allow for verbose printing. 
Currently, there is only one level of printing, so either it is on of off. 

\index{SetVerbose}
\begin{intrinsics}
SetVerbose(MonStgElt, RngIntElt) : -> 
\end{intrinsics}

{\tt SetVerbose} is a built in Magma function, but with this package, this intrinsic accepts the string {\tt "Multilinear"} and an integer in $\{0,1\}$. 

We have included an intrinsic to check which version of eMAGma you have attached in Magma.

\index{eMAGmaVersion}
\begin{intrinsics}
eMAGmaVersion() : -> MonStgElt
\end{intrinsics}

Returns the version number for the eMAGma package attached in Magma.

\chapter{Tensors}

\input{tensors.tex}
\input{alg-invariants.tex}

\chapter{Tensor spaces}

\input{tensor-spc-cat.tex}

\chapter{Exceptional tensors}

\input{exceptional.tex}

\chapter{Some examples}

\input{longer-exs.tex}

\appendix

\chapter{Cyclic algebras and their modules}

\input{cyclic.tex}

\backmatter

\begin{bibdiv}
\begin{biblist}

\bib{Magma}{article}{
   author={Bosma, Wieb},
   author={Cannon, John},
   author={Playoust, Catherine},
   title={The Magma algebra system. I. The user language},
   note={Computational algebra and number theory (London, 1993)},
   journal={J. Symbolic Comput.},
   volume={24},
   date={1997},
   number={3-4},
   pages={235--265},
   %issn={0747-7171},
   review={\MR{1484478}},
}

\bib{BW:grps-tensor}{article}{
   author={Brooksbank, Peter A.},
   author={Wilson, James B.},
   title={Groups acting on tensor products},
   journal={J. Pure Appl. Algebra},
   volume={218},
   date={2014},
   number={3},
   pages={405--416},
   issn={0022-4049},
   review={\MR{3124207}},
}

\bib{BW:Module-iso}{article}{
   author={Brooksbank, Peter A.},
   author={Wilson, James B.},
   title={The module isomorphism problem reconsidered},
   journal={J. Algebra},
   volume={421},
   date={2015},
   pages={541--559},
   review={\MR{3272396}},
}

\bib{FMW}{article}{
   author={First, Uriya},
   author={Maglione, Joshua},
   author={Wilson, James B.},
   title={Polynomial identity tensors and their invariants},
   note={in preparation},
}

\bib{Landsberg:tensors}{book}{
   author={Landsberg, J. M.},
   title={Tensors: geometry and applications},
   series={Graduate Studies in Mathematics},
   volume={128},
   publisher={American Mathematical Society, Providence, RI},
   date={2012},
   pages={xx+439},
   review={\MR{2865915}},
}

\bib{Lee:geom}{book}{
   author={Lee, John M.},
   title={Introduction to smooth manifolds},
   series={Graduate Texts in Mathematics},
   volume={218},
   edition={2},
   publisher={Springer, New York},
   date={2013},
   pages={xvi+708},
   review={\MR{2954043}},
}

\bib{Payne:elation-grps}{article}{
   author={Payne, Stanley E.},
   title={Finite groups that admit Kantor families},
   conference={
      title={Finite geometries, groups, and computation},
   },
   book={
      publisher={Walter de Gruyter GmbH \& Co. KG, Berlin},
   },
   date={2006},
   pages={191--202},
   review={\MR{2258010}},
}

\bib{Malcev}{book}{
   author={Mal{\cprime}cev, A. I.},
   title={Foundations of linear algebra},
   series={Translated from the Russian by Thomas Craig Brown; edited by J.
   B. Roberts},
   publisher={W. H. Freeman \& Co., San Francisco, Calif.-London},
   date={1963},
   pages={xi+304},
   review={\MR{0166200}},
}

\bib{Schafer}{book}{
   author={Schafer, Richard D.},
   title={An introduction to nonassociative algebras},
   series={Pure and Applied Mathematics, Vol. 22},
   publisher={Academic Press, New York-London},
   date={1966},
   pages={x+166},
   review={\MR{0210757}},
}

\bib{Weyl}{book}{
	author={Weyl, Herman},
	title={The theory of groups and quantum mechanics},
	publisher={Dover, New York},
	year={1950},
}

\bib{Wilson:division}{article}{
   author={Wilson, James B.},
   title={Division, adjoints, and dualities of bilinear maps},
   journal={Comm. Algebra},
   volume={41},
   date={2013},
   number={11},
   pages={3989--4008},
   review={\MR{3169502}},
}

\end{biblist}
\end{bibdiv}

\printindex


\end{document}
